The Efficient Handling of Guards \\in the Design of RPython's Tracing JIT

### 2012-09-07 talk/vmil2012/paper.tex
tweak colors

\definecolor{commentgray}{rgb}{0.3,0.3,0.3}
\definecolor{darkgray}{rgb}{0.5,0.5,0.5}
\definecolor{lightgray}{rgb}{0.75,0.75,0.75}

@@

\bigtodo{reviewer b: One missing data set in the empirical study
is excution time performance info for the
various guard implementation choices.
The empirical data focuses on space not
time.}

\bigtodo{reviewer c:
I would have liked to see an evaluation based on execution time rather than
operations. I do not have a good sense of the relative cost of different
operations, and from my experience know that it can be misleading to use such a
measure.}

\bigtodo{reviewer c:
For all of the results some aggregate values would be useful (max/min, etc.)
}

@@

\bigtodo{for comparison we should add the total number of guards per benchmark to one of the tables, and maybe also the number of traces}

>>>>

\definecolor{commentgray}{rgb}{0.3,0.3,0.3}
\definecolor{darkgray}{rgb}{0.6,0.6,0.6}
\definecolor{lightgray}{rgb}{0.75,0.75,0.75}

@@

@@
